Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on
Pottier and Simonet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in \origLang's original
formulation and theorems.  We discuss what would be involved in completing the
proof and how this relates to other work.

@@

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and have seen multiple extensions over the years.  Although
it's pretty certain extensions to these languages that are published are
correct, errors to creep into even the most scrutinized of paper results (as we have observed in this project), and so requiring these extensions to come with mechanized proofs of correctness before incorporation into a verified compiler would help ensure that the language updates will not invalidate pre-existing security
properties of the language.

>>>>

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on
Pottier and Simonet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in \origLang's original
formulation and theorems.  Furthermore, we discuss what would be involved in
completing the proof and how this relates to other work.

@@

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and have seen multiple extensions over the years.  Although
it's pretty certain that extensions to these languages that are published are
correct, errors to creep into even the most scrutinized of paper results (as we
have observed in this project), and so requiring these extensions to come with
mechanized proofs of correctness before incorporation into a verified compiler
would help ensure that the language updates will not invalidate pre-existing
security properties of the language.
